The Formation and Evolution of Compact Core Galaxies in the RESOLVE Survey

### 2016-04-12 paperdraft.tex
updates to paper

With its improved redshift recovery, RESOLVE is complete down to absolute $r$-band magnitudes of $-17.33$ and $-17.0$ for the A and B semesters, respectively. We can convert these absolute magnitude limits into stellar mass limits: M$_{\star} \sim 10^{8.9}$ \Msun for the A semester and M$_{\star} \sim 10^{8.7}$ \Msun in the B semester (see Figure 7 in \citet{Eckert2015B}). In Figure 1, we plot the stellar masses against the deconvolved \Reff (see \autoref{deconv}) and see that these limits allow us to reach down to CSSs with sizes similar to cEs. We are not able to recover UCD-like objects, but this should not matter since we are studying CSSs as a whole in order to investiage evolutionary sequences.

@@

\noindent In order to get accurate \Reff measurements for all galaxies in the RESOLVE sample, we use Galfit \citep{Peng2002} to deconvolve the seeing point spread function (PSF) and perform one and two component fits on high-resolution imaging. Deconvolution is important as the smallest galaxies in RESOLVE are most effected by seeing, and accurate radii measurements are crucial for our science. High imaging resolution for the galaxies in RESOLVE is necessary to resolve compact cores down to cE-like radii. Thus, for both RESOLVE-A and RESOLVE-B, we use publicly-available UKIDSS Large Area Survey \citep{Lawrence2007} $Y$-band data, which offers $\sim0.8''$ seeing resolution corresponding to $\sim350$pc at RESOLVE distances.

The first step in this process is to create PSFs for each image. My process is as follows:

\begin{enumerate}

\item We begin by running Source Extractor on the image to identify every object and get estimates for each object's flux, elongation, ellipticity, radius, and \texttt{class\_star}.

@@

\noindent Once the PSF is complete, we fit a crude 2D Gaussian to it to determine a rough estimate seeing FWHM. The average seeing FWHM is $\sim 0.9''$, only slightly worse than the $\sim 0.8''$ seeing expected for UKIDSS imaging.

The next steps involve the creation of items necessary for Galfit to run properly. This includes an image mask, a constraint file, and starting guesses for the parameters being fit. The image mask is made by running each image through Source Extractor and using its output list of sources and their sizes to create a binary image of the objects to mask. The

With the one and two component fits from Galfit in hand, we compare the reduced chi-square values for each fit and determine where the two component fit provides a significant improvement to the reduced chi-square of the one component fit. With each galaxy now having either a one or two component fit, we select objects that have a one component radius $<800$ pc  or have a two component core radius $<800$ pc. The core will be the smaller of the two components fit by Galfit.

@@

\subsection{Gas Content}
\noindent * look into g/s ratios \\
* reference Dave and Katie's work here

\subsection{Metallicities}
\noindent * reference AIMSS III paper on what metallicities could tell us about formation scenarios

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{
  Acknowledgments. 
}

>>>>

With its improved redshift recovery, RESOLVE is complete down to absolute $r$-band magnitudes of $-17.33$ and $-17.0$ for the A and B semesters, respectively. We can convert these absolute magnitude limits into stellar mass limits: M$_{\star} \sim 10^{8.9}$ \Msun for the A semester and M$_{\star} \sim 10^{8.7}$ \Msun in the B semester (see Figure 7 in \citet{Eckert2015B}). In Figure 1, we plot the stellar masses against the deconvolved \Reff\ (see \autoref{deconv}) and see that these limits allow us to reach down to CSSs with sizes similar to cEs. We are not able to recover UCD-like objects, but this should not matter since we are studying CSSs as a whole in order to investiage evolutionary sequences.

@@

\noindent We begin our analysis by deriving seeing-corrected \Reff\ measurements for all galaxies in the RESOLVE sample. For this task we employ \textsc{Galfit} \citep{Peng2002} to deconvolve the seeing point spread function (PSF) and to perform one and two component fits on each galaxy. Deconvolution is especially important since the smallest galaxies in RESOLVE are most effected by seeing, and accurate radii measurements are crucial for the study of these objects.

\textsc{Galfit} needs the following input files to function correctly: an initial input file, an image of the galaxy, a PSF image, an image mask, and a constraint file.  We obtain/construct these items as follows:

\begin{description}

\item[The initial input file]{The initial input file tells \textsc{Galfit} where to find the image, PSF, mask, and constraint, and also holds the initial guesses for our fit parameters. These initial parameters can just be rough guesses, but for our purposes, we use the previously derived photometric data for RESOLVE galaxies as our initial guesses (see \autoref{phot} for more details). For the one component fits, we set up our input file to have a section for measuring the value of the sky background, and another section for fitting a S\'ersic profile to galaxy. The two component fits with have three sections -- the sky and S\'ersic as in the one component fits, plus a second S\'ersic fit. }

\item[Imaging data]{We use publicly-available high resolution $Y$-band imaging from the UKIDSS Large Area Survey \citep{Lawrence2007}. This data set was chosen because it covers both RESOLVE-A and RESOLVE-B and offers $\sim0.8''$ seeing resolution corresponding to $\sim350$pc at RESOLVE distances in turn letting us span down to the sizes of cE-like galaxies. The $Y$ band is advantageous too, since it probes the underlying stellar population and will not skew our measurements to larger radii if the galaxy is currently experiencing a starburst. We download $\sim10'\times10'$ images of each galaxy from the WFCAM Science Archive\footnote{\url{was.roe.ac.uk//}}}. While \textsc{Galfit} does not require images this large to operate normally, we choose this size so that there will be more stars in the field of view which is useful for constructing a PSF. There are  only XX galaxies in RESOLVE that do not have UKIDSS imaging and thus are excluded from our analysis. Visual inspection of these galaxies indicate that they would most likely not be classified as CCGs anyways.

\item[The PSF image]{We build our PSF image via the following steps.
\begin{enumerate}

\item We begin by running Source Extractor on the image to identify every object in the frame, including stars, galaxies, and even sometimes hot pixels. Source Extractor outputs a .txt file that has estimates of each object's flux, elongation, ellipticity, radius, and \texttt{class\_star}.

@@

\noindent Our last step is to fit a 2D Gaussian to the PSF to determine a rough estimate seeing full width half max (FWHM), as a sanity check. We find that the average FWHM for all PSFs is $\sim 0.9''$, only slightly worse than the $\sim 0.8''$ seeing expected for UKIDSS imaging. \textsc{Galfit} uses this PSF image to deconvolve the galaxy light profile from the seeing, thereby removing the effects of atmospheric scattering of the galaxy light as the data was taken.}

\item[The mask image]{The first step is to create a mask image that has the same dimensions as our input image with each pixel value as zero. We again use Source Extractor to compile a list of all the objects in the input image, and then use this list to replace the pixel values in our mask with one. We replace the areas of the mask that have detected sources with ones, thus creating a binary image. \textsc{Galfit} uses the mask image to }

\item[The constant file]{The constraint file hosts the limits we are willing to accept for our fits. We fit on the following galaxy parameters: x \& y position in the image, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle. The constraints in place for these variables are listed in \autoref{constrtable}.}

\end{description}

\begin{table}[htdp]
\begin{center}
\begin{tabular}{cc} \hline
parameter & constaint  \\ \hline
x \& y position & $\pm5$ pixels from input value \\
integrated magnitude & 0 -- 40 \\ 
\Reff\ & 0.2 -- 750 pixels \\ 
S\'ersic n & 0.1 -- 8 \\ 
axial ratio & 0 -- 1 \\
position angle & -360 -- 360 \\ \hline

\end{tabular}
\end{center}
\caption{Summary of the constraints imposed on our \textsc{Galfit} models.}
\label{constrtable}
\end{table}%

With the one and two component fits from \textsc{Galfit} in hand, we compare the reduced chi-square values for each fit and determine where the two component fit provides a significant improvement to the reduced chi-square of the one component fit. With each galaxy now having either a one or two component fit, we select objects that have a one component radius $<800$ pc  or have a two component core radius $<800$ pc. The core will be the smaller of the two components fit by \textsc{Galfit}.

@@

@@

\section{Future Work}
%\subsection{Gas Content}
%\noindent * look into g/s ratios \\
%* reference Dave and Katie's work here

%\subsection{Metallicities}
%\noindent * reference AIMSS III paper on what metallicities could tell us about formation scenarios
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{
  Acknowledgments. 
}
